A numerical study of fixation probabilities for strategies in the Iterated Prisoner's Dilemma

### 2017-04-16 tex/main.tex
Add a number of visualisations.
- Heatmaps
- Histograms

Also: tidy the nb.

% TODO Compare fixation rates to neutral fixation 1/2 (because we're in the N/2)
% case.

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{../img/median_rank_vs_population_size_std.pdf}
    \caption{Median (inverse) rank of players against population size}
    \label{fig:ranks_v_size_standard}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{../img/median_rank_vs_population_size_noisy.pdf}
    \caption{Median (inverse) rank of players against population size with noise}
    \label{fig:ranks_v_size_noisy}
\end{figure}

>>>>

Figures~\ref{fig:fixation_heatmap_std} and~\ref{fig:fixation_heatmap_noise}
shows the fixation rates of each player on the y axis against each player on the
x axis.

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_2_std.pdf}
        \caption{\(N=2\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_4_std.pdf}
        \caption{\(N=4\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_6_std.pdf}
        \caption{\(N=6\)}
    \end{subfigure}%

    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_8_std.pdf}
        \caption{\(N=8\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_10_std.pdf}
        \caption{\(N=10\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_12_std.pdf}
        \caption{\(N=12\)}
    \end{subfigure}%

    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_14_std.pdf}
        \caption{\(N=14\)}
    \end{subfigure}%
    \caption{Fixation probabilities of all strategies}
    \label{fig:fixation_heatmap_std}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_2_noise.pdf}
        \caption{\(N=2\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_4_noise.pdf}
        \caption{\(N=4\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_6_noise.pdf}
        \caption{\(N=6\)}
    \end{subfigure}%

    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_8_noise.pdf}
        \caption{\(N=8\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_10_noise.pdf}
        \caption{\(N=10\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_12_noise.pdf}
        \caption{\(N=12\)}
    \end{subfigure}%

    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_14_noise.pdf}
        \caption{\(N=14\)}
    \end{subfigure}%
    \caption{Fixation probabilities of all strategies (with noise)}
    \label{fig:fixation_heatmap_std}
\end{figure}

Figure~\ref{fig:histograms_all_fixation_rates_std}
and~\ref{fig:histograms_all_fixation_rates_noise} show the distribution of the
fixation rates for all strategies.

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=.8\textwidth]{../img/histograms_all_fixation_rates_std.pdf}
    \caption{Distribution of fixation rates for all players}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=.8\textwidth]{../img/histograms_all_fixation_rates_noise.pdf}
    \caption{Distribution of fixation rates for all players (noise)}
\end{figure}

Figure~\ref{fig:histograms_median_fixation_rates_std}
and~\ref{fig:histograms_median_fixation_rates_noise} show the distribution of the
fixation rates for all strategies.

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=.8\textwidth]{../img/histograms_median_fixation_rates_std.pdf}
    \caption{Distribution of median fixation rates for all players}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=.8\textwidth]{../img/histograms_median_fixation_rates_noise.pdf}
    \caption{Distribution of median fixation rates for all players (noise)}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{../img/median_rank_vs_population_size_std.pdf}
    \caption{Median rank of players against population size}
    \label{fig:ranks_v_size_standard}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{../img/median_rank_vs_population_size_noisy.pdf}
    \caption{Median  rank of players against population size with noise}
    \label{fig:ranks_v_size_noisy}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{../img/relationship_between_median_ranks_std.pdf}
    \caption{Relationship between Median rank for population size}
    \label{fig:relationship_ranks_v_size_standard}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{../img/relationship_between_median_ranks_noisy.pdf}
    \caption{Relationship between Median rank for population size with noise}
    \label{fig:relationship_ranks_v_size_noise}
\end{figure}
